\documentclass[11pt,oneside,letterpaper]{article}

\setlength{\parindent}{2eM}
\setlength{\parskip}{0ex}

\title{\LaTeX{} Assignment 1}
\date{January 13, 2023}
\author{Surina Marwaha}

\begin{document}

\pagestyle{plain}
\maketitle

\begin{center}
	\rule{33eM}{0.2ex}
\end{center}

\noindent\textbf{Exercise 1}
\newline\newline
As shown on page 5 of the textbook, special characters such as \$, \{, \~, and \% are produced with a preceding backslash. Another way to produce these characters is to use the \verb+\verb#stuff#+command, which typesets ``stuff'' verbatim (including spaces and special characters) in a typewriter font. The beginning and ending \# delimiters can be replaced with other non-letter characters such as \^, \textbackslash, 4, or !.

Only use \verb+\verb+ verb to display short strings verbatim. Do not use \verb+\verb+ to change the font. For that purpose there is the command \verb+\textt{text}+ which prints ``text'' in a typewriter font.

There are other commands which change the font: \textbf{bold}, \textsf{sans serif}, \textsl{slanted}, \textit{italicized}, and \textsc{small caps} are produced by \verb+\textbf{}+, \verb+\textsf{}+, \verb+\textsl{}+,
\verb+\textit{}+, and \verb+\textsc{}+. Within any of these fonts, words can be \emph{emphasized}
using \verb+\emph{}+. For instance, \textbf{this is \textit{special} bold text}. Text can also be
\underline{underlined} with \verb+\underline{}+. Use special fonts sparingly, if at all!

The compiler tries to align the first and last characters in consecutive lines in a paragraph. As a result, the space between words can vary from line to line. Naïve \LaTeX{}ers sometimes try to change this spacing by forcing breaks
with commands such as \verb+\newline+ or \verb+\\+. Don’t do this! 

Some users may try to change the spacing between paragraphs using commands such as \verb+\\[4cm]+ or \verb+\vspace{1.1in}+. These last commands produce vertical spaces of 4 centimeters and 1.1 inches, respectively. Using these commands frequently is the hallmark of poor \LaTeX{}er.

\newpage

\noindent\textbf{Exercise 2}
\newline\newline
Sometimes I worry when I reach in to take tofu out of the oven, that the midnight kitchen gremlins will shut me inside, and my last words will be something like ``\^a\"a\H a\t aa\'a\d a\=a\u a\aa ---'' and I'll melt into the 300\textdegree{}F and then the gremlins will eat all my tofu after midnight and kill my roommates in their sleep \ldots

\end{document}