% The [10pt] option gives the font size.
\documentclass[10pt]{article}

% '\parindent' controls the indentation at the beginning of a paragraph.  The 'eM' is a
% unit of measure in typography that was traditionally derived from the width of 'M'.
\setlength{\parindent}{0eM}

% '\parskip' controls the white space between paragraphs.  The 'plus' and 'minus' are
% optional specifications that tell the compiler how much leeway there is when formatting
% paragraphs on a page.  The 'ex' is a unit of measure equal to the height of 'x'.
\setlength{\parskip}{3ex plus 1ex minus 1ex}

\title{\LaTeX{} Typesetting}
\author{\textsc{mathematics 351 syllabus}}
\date{}

\begin{document}

\maketitle

% '\thispagestyle{empty}' suppresses the page number on this page.  To suppress all page
% numbers place '\pagestyle{empty}' before the '\begin{document}'.
\thispagestyle{empty}

% '\rule{width}{height}' produces a line.
\rule{\textwidth}{.01ex}

% The '\@' command that appears after a period tells the compiler that the period does not
% end a sentence and should not be spaced as if it did.
\textbf{Instructor:} Anthony Mendes.  Call me Tony or Dr.\@ Mendes.

\textbf{Email:} \texttt{aamendes@calpoly.edu}

\textbf{Office hours:} Mondays from 12:30pm until 2pm and Thursdays from 12pm until 1:30pm
in Building 25 Room 202.

\textbf{Website}: The website \texttt{https://anthonymendes.github.io/351.html} has course
information and many \LaTeX{} files.  Assignments are turned in on Canvas.

\textbf{Text}: Our textbook is \textsl{The Not So Short Introduction to \LaTeXe} by
Oetiker, Partl, Schlegl, and Hyna.  The book is available on our website.  Some course
topics cannot be found in the text.

\textbf{Content:} Each week we will introduce new \LaTeX{} concepts.  By the end of the
course, you will be able to use \LaTeX{} to create professional looking research articles,
presentations, posters, classroom materials, and r\'esum\'es.

\textbf{Assignments:} Each week there will be an assignment.  All source files and the
\texttt{.pdf} output for each assignment are to be submitted to Canvas.

\textbf{Grading:} A student who completes 7 out of the 9 assignments on time and with
acceptable quality will be assigned ``Credit'' for the course.  Otherwise a student will
receive ``No Credit''.  There are no exams.

\textbf{\LaTeX{er} of the week:} Each week one student with an exemplary assignment will
be recognized as our ``\LaTeX{er} of the week''.  Their name and assignment will be
located in a place of honor on our web site for all to envy and admire.  Please let me
know if you do not want your name or work on our web site.

\rule{\textwidth}{.02ex}

\end{document}