\documentclass[11pt]{article}

\title{How to compile \LaTeX{} files}
\author{}
\date{}

\begin{document}

\maketitle

\LaTeX{} files can be edited and compiled locally on your personal computer.
This is the preferred option for serious projects such as books, research
publications and presentations.  There are many free options for downloading
and installing \LaTeX{} on each operating system.
\begin{itemize}
\item Windows users can use MikTeX.  See \texttt{miktex.org/}.

\item Apple users can use MacTex.  See \texttt{www.tug.org/mactex/}.

\item Linux users may find \LaTeX{} is already installed on their machine.  If
  not, Debian or Ubuntu users can enter \texttt{sudo apt-get install
    texlive-full} in a terminal.
\end{itemize}
\LaTeX{} files can also be edited and compiled on a third party web site such
as \texttt{www.overleaf.com}.  This is a fine option to get up and running
quickly.

Use \LaTeX{} by first opening and editing a plain text file.  Save the file
with the \texttt{.tex} extension.  The \texttt{.tex} file can be compiled to
produce a \texttt{.pdf} file using either \texttt{pdflatex} or
\texttt{xelatex}.  The choice of compiler is usually an option in a drop down
menu in \LaTeX{} software packages or, if using the command line, can be
invoked by entering \texttt{pdflatex filename.tex} or \texttt{xelatex
  filename.tex} in a terminal.  The \texttt{pdflatex} option is faster and more
established, but the \texttt{xelatex} option is better at handling fonts.

I use Emacs with the Auctex package to edit \texttt{.tex} files and compile
with \texttt{xelatex}.  This is probably the best way to write \LaTeX{} code,
but requires knowledge of Emacs and is not for beginners.

\end{document}
