\documentclass{article}

\usepackage{amssymb,enumitem,xcolor,mathspec,titlesec}
\usepackage[margin=1in]{geometry}

% Color palette and fonts are specified at
% https://ucm.calpoly.edu/visual-identity

\definecolor{White}{HTML}{FEFEFE}
\definecolor{Black}{HTML}{010101}
\definecolor{CalPolyGreen}{HTML}{154734}
\definecolor{CalPolyGold}{HTML}{C69214}
\definecolor{DigitalGold}{HTML}{BD8B13}
\definecolor{StadiumGold}{HTML}{F8E08E}
\definecolor{PolyCanyon}{HTML}{F2C75C}
\definecolor{DexterGreen}{HTML}{A4D65E}
\definecolor{FarmersMarket}{HTML}{3A913F}
\definecolor{SkyBlue}{HTML}{B5E3D8}
\definecolor{SurfBlue}{HTML}{5CB8B2}
\definecolor{Serenity}{HTML}{D3E3F4}
\definecolor{MorroBlue}{HTML}{ABCAE9}
\definecolor{MissionBeige}{HTML}{E4E1D1}
\definecolor{PismoSand}{HTML}{CAC7A7}
\definecolor{CoastSage}{HTML}{B6CCC2}
\definecolor{Sycamore}{HTML}{789F90}
\definecolor{KennedyGray}{HTML}{8E9089}
\definecolor{SealGray}{HTML}{54585A}
\definecolor{HeritageOrange}{HTML}{FF6A39}
\definecolor{HeritageOrange50}{HTML}{FEB898}
\definecolor{Avocado}{HTML}{D0DF00}
\definecolor{Avocado50}{HTML}{EBED8A}

\usepackage[colorlinks = true,
urlcolor = DigitalGold,
linkcolor = DigitalGold,
citecolor = DigitalGold]{hyperref}

% Be sure to change this if the following fonts are not on your machine
\setmathsfont(Digits,Latin,Greek)[Numbers={Lining,Proportional}]{Source Sans Pro}
\setmainfont{Source Sans Pro}
\setmonofont{Source Code Pro}

\color{SealGray}

\setlist[itemize]{itemsep=-1ex,topsep=0.5ex,parsep=1ex}
\setlength{\parindent}{0ex}
\setlength{\parskip}{0ex}

\def\labelitemi{\color{CalPolyGreen}$\cdot$}

\titleformat*{\section}{% \fontspec{Utopia} \selectfont
  \large \bfseries \color{CalPolyGreen}}

\pagestyle{empty}

\begin{document}

\begin{center}
  {\fontsize{1.5cm}{1.5cm}
    \color{CalPolyGreen}
    \fontspec{Alte DIN 1451 Mittelschrift}
    \selectfont
    \textbf{Musty Mustang}}

  \bigskip

  \textsf{mmustang@calpoly.edu}
  \qquad
  \href{https://mmustang.github.io/}{\textsf{https://mmustang.github.io/}}
  \qquad
  \textsf{\begin{small}(805)756-1699\end{small}}
\end{center}

\section*{Objective}

Secure a data scientist position with an innovative organization in the San
Francisco bay area.

\section*{Education}

\begin{description}
\item[Bachelor of Science in Mathematics] Cal Poly, San Luis Obispo, CA.
  Spring 2025 (expected).

Relevant course work includes advanced coursework in

\begin{itemize}
\item Data Science
\item Numerical Analysis
\item Matrix and Linear Algebra
\item Nonparametric and Parametric Statistics
\item Design and Analysis of Algorithms
\end{itemize}

Senior project analyzed Neilsen television ratings data from the Tennis Channel
to determine which tennis matches would yield the highest ratings.  The project
involved significant data processing, computer programming, various regression
models, and the singular value decomposition.
\end{description}

\section*{Employment}

\begin{description}
\item[Intern Software Developer]

  Amazon-SLO, San Luis Obispo, CA.  Summer 2022.

  Responsible for preparing data acquired from user shipping addresses in order
  to decide the optimal locations for new shipping centers.

\item[Research Assistant]

  Mathematics Department, Cal Poly, San Luis Obispo, CA.  Summer 2021.

  Hand selected to work in a paid summer research position under the direction
  of Professor Anthony Mendes.  Our project was to investigate the relationship
  between the Robinson Schensted algorithm and a theorem concerning permutation
  inversions.

\item[Workshop Leader]

  Mathematics Department, Cal Poly, San Luis Obispo, CA.  2020--2023.

  Led discussion sections for students in Calculus I, II, and III.  Consistently
  rated by students as excellent with clear communication skills.
\end{description}

\section*{Technical Skills}
\begin{itemize}
\item Python with pandas and scikit-learn
\item \LaTeX{} typesetting
\item Significant formal training in mathematics
\item Some experience with Java, C++
\end{itemize}

\section*{Activities}
\begin{itemize}
\item Society of Women Engineers, 2020--2024
\item Math Club, 2020--2024
\item Cal Poly Active Minds club, 2020--2024
\item Dorm resident advisor, 2021--2022
\item Piano enthusiast
\end{itemize}

\end{document}
